On mortality of the dead and OLS

### 2018-01-22 ols.Rmd
add plot for the dead

```{r standards}
fit <- coxph(Surv(enter, exit, event) ~ strata(region, sex), data = ols)
par(las = 1)
plot(survfit(fit), fun = "cumhaz", col = 1:4, lty = 1:4, xlab = "Years after 60.", ylab = "Cum. hazards", axes = FALSE)
axis(1, at = c(0, 9, 13, 20, 30, 40))
axis(2, at = c(0, log(2), 3, 5), labels = c("0", "log(2)", "3", "5"))
box()
legend("topleft", legend = levels(strata(ols$region, ols$sex)), col = 1:4, lty = 1:4)
abline(h = 0)
abline(h = log(2), lty = 2)
```

@@

# Conclusion

>>>>

```{r standards, fig.cap = "Full data."}
fit <- coxph(Surv(enter, exit, event) ~ strata(region, sex), data = ols)
par(las = 1)
plot(survfit(fit), fun = "cumhaz", col = 1:4, lty = 1:4, xlab = "Years after 60.", ylab = "Cum. hazards", axes = FALSE)
axis(1, at = c(0, 9, 13, 20, 30, 40))
axis(2, at = c(0, log(2), 3, 5), labels = c("0", "log(2)", "3", "5"))
box()
legend("topleft", legend = levels(strata(ols$region, ols$sex)), col = 1:4, lty = 1:4)
abline(h = 0)
abline(h = log(2), lty = 2)
```

@@

## Mortality of the dead

Median life becomes about two years shorter for the "dead". Furthermore, mortality continue to rise after age 90, in contrast to
what happens with full data. I suspect many too late censored in the high ages, a problem with the data registration. I will return with 
a study of mortality after age 90 in a coming post.

```{r nonstandards, fig.cap = "Sampling of the dead."}
sfit <- coxph(Surv(enter, exit, event) ~ strata(region, sex), data = sols)
par(las = 1)
plot(survfit(sfit), fun = "cumhaz", col = 1:4, lty = 1:4, xlab = "Years after 60.", ylab = "Cum. hazards", axes = FALSE)
axis(1, at = c(0, 7, 11, 20, 30, 40))
axis(2, at = c(0, log(2), 3, 5, 7), labels = c("0", "log(2)", "3", "5", "7"))
box()
legend("topleft", legend = levels(strata(ols$region, ols$sex)), col = 1:4, lty = 1:4)
abline(h = 0)
abline(h = log(2), lty = 2)
```

```{r }
plot(survfit(sfit), col = 1:4, lty = 1:4, xlab = "Years after 60, the dead.", 
     ylab = "Remaining fraction", axes = FALSE)
axis(1, at = c(0, 7, 11, 20, 30))
axis(2, at = c(0, 0.5, 1), las = 1)
box()
legend("topright", legend = levels(strata(ols$region, ols$sex)), col = 1:4, lty = 1:4)
abline(h = 0)
abline(h = 0.5, lty = 2)
```

We can also here make an exact calculation, which results in

```{r exactkis}
x <- survfit(sfit)
x
```
# Conclusion
